---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753RYANFITZ24)
```

# Introduction

This is a project made for MATH-4753 Spring 2024 that has several functions added over the year.

## fire

fire is a data set collected concerning home damage from fire

```{r}
MATH4753RYANFITZ24::fire
```


## mybin

creates a binomial distribution and puts the result into a barplot

```{r}
MATH4753RYANFITZ24::mybin(iter = 1001, n = 32, p = .45)
```


## myboot2

bootstrap re sampling to estimate the sampling distribution of a statistic and makes a confidence interval.

```{r}
MATH4753RYANFITZ24::myboot2(iter = 100, x = rnorm(99), fun = "mean", alpha = 0.05, cx = 1.5)
```

## mycltp

Central Limit theorem for a Poisson distribution

```{r}
#MATH4753RYANFITZ24::mycltp(n=10,iter=100, lambda = 4)
```

## myf

Model y = b0 + b1x + b2(x-xk)*(x>xk) with x_k being 18

```{r}
MATH4753RYANFITZ24::myf(32, coef = c(1, 2, 3))
```

## mymlnorm

maximum likelihood estimation for a normal distribution

```{r}
mymlnorm(x=c(10,12,13,15,12,11,10),mu=seq(10,14,length=1000),
sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```


## myncurve

Plots the normal distribution and shades the area under the curve up to a. Also returns the area under the curve up to a.

```{r}
MATH4753RYANFITZ24::myncurve(mu=10,sigma=5, a=6)
```


## myquad

Quadratic function x^2 - 5*x + 6 with a given x

```{r}
MATH4753RYANFITZ24::myquad(x = 20)
```


## ntickets

calculates the number of tickets to be sold when the number of seats in the flight is N and the probability of a "show" is p and gamma is the probability a plane will be truly overbooked

```{r}
MATH4753RYANFITZ24::ntickets(N=500, gamma = 0.03, p = 0.90)
```

